LA ranks

### 2024-06-12 src/la_ranks_n1.Rmd
mac

```{r}
# get LA for the UK
path.geo <- paste0(path, "/data/raw/Local_Authority_Districts_(December_2021)_UK_BUC.geojson")
la <- readOGR(path.geo)

la.names <- la@data %>% 
  dplyr::select(LAD21CD, LAD21NM) %>% 
  rename(ladcd = LAD21CD,
         ladnm = LAD21NM)

df <- df %>% left_join(la.names)
# source: https://geoportal.statistics.gov.uk/
```

@@

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank))) %>% 
  #ungroup() %>% summarise(q = quantile(abs(diff_1st), .95, na.rm = T)) 
  # t= 2000: q.95 = 199.5, q.9 = 168, q.1 = 7, q.05 = 3.75. **abs()**
  # t= 1996: q.95 = 257.125, q.9 = 232.25, q.1 = 17.75, q.05 = 6.875. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 199.5, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

@@

## Ranks websites 2000 and 2012 only

@@

## Websites per year

@@

## Ranks websites per firm all period

>>>>

```{r}
# get LA for the UK
path.geo <- paste0(path, "/data/raw/Local_Authority_Districts_(December_2021)_UK_BUC.geojson")
la <- st_read(path.geo)
# source: https://geoportal.statistics.gov.uk/

la.names <- la %>% 
  dplyr::select(LAD21CD, LAD21NM) %>% 
  rename(ladcd = LAD21CD,
         ladnm = LAD21NM)

df <- df %>% left_join(la.names) %>% 
  dplyr::select(-geometry)
# source: https://geoportal.statistics.gov.uk/
```

@@

df %>% group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  filter(year==t | year == 2012) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank))) %>% 
  # ungroup() %>% summarise(q = quantile(abs(diff_1st), .1, na.rm = T)) 
  # t = 2000: q.95 = 194.5, q.90 = 168.5, q.1 = 9, q.05 = 3.75. **abs()**, 12/6/2024
  # t = 2000: q.95 = 199.5, q.9 = 168, q.1 = 7, q.05 = 3.75. **abs()**
  # t = 1996: q.95 = 257.125, q.9 = 232.25, q.1 = 17.75, q.05 = 6.875. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 194.5, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 3.75, .8, 0.1)) %>%

  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

@@

## Average ranks websites per firm t and 2012 only

# change percentile in out.path and mutate(alpha = ifelse(abs(diff_1st)

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95_av.png")

df %>% 
  mutate(period = ifelse(year < 1999, 1, 
                         ifelse(year > 2009, 3, 2))) %>%
  group_by(ladcd, period) %>%
  mutate(n_by_firm = ifelse(period != 2, mean(n_by_firm), n_by_firm)) %>% 
  filter(year > 1997 & year < 2011) %>% 
  group_by(year) %>% 
  mutate(rank = rank(desc(n_by_firm))) %>% # or n_by_firm
  ungroup() %>% 
  filter(year==1998 | year == 2010) %>% 
  arrange(ladcd, year) %>% 
  group_by(ladcd) %>% 
  #mutate(diff_1st = -diff(rank))
  mutate(diff_1st = -(rank-lag(rank))) %>%

  # ungroup() %>% summarise(q = quantile(abs(diff_1st), .1, na.rm = T)) 
  # q.95 = 253, q.9 = 214, q.1 = 11, q.05 = 3.75. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) > 253, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 3.75, .8, 0.1)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.1, alpha)) %>%
  mutate(label = ifelse(alpha==.1, "", ladnm)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(colour = "red") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  # geom_text(#data = df %>% filter(year == 2012),
  #           aes(x = Inf, label = label), size = 4, hjust = 0)  # x = 2012 + .1
  geom_text_repel(aes(label = label),
                  na.rm = TRUE, 
                  size = 2,
                  nudge_x = 2, nudge_y = 1,
                  direction = "y", hjust = "left") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.position="none") +
  scale_x_continuous("year", 
                     #limits = c(1998, 2010), 
                     breaks=c(1998, 2002, 2006, 2010),
                     labels = c("1996-98","2002", "2006", "2010-12"))
ggsave(out.path)
```

## Not used

### Ranks websites 2000 and 2012 only

@@

### Websites per year

@@

### Ranks websites per firm all period
